---
title: "Untitled"
author: Aaron Gullickson
format:
  html: default
  pdf: default
  docx: default
execute: 
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
#| output: false

library(tidyverse)
library(gt)
load("stat_data/popularity.RData")
```

# Compare number of sports by grade

## Second level header

### Third level header

```{r}
# this won't work on render because we haven't defined x in the document
#x * 2
```

#### Fourth level header

How do **number** of *sports* differ by _grade_ level?

- I don't know
- Another point
- Bob
  - Or Amanda?

1. First **point**
1. Second point
1. Third point

> I have sworn upon the altar of God eternal hostility against every form of tyranny over the mind of man

This is a paragraph.

This is another paragraph.

This is a paragraph.
  This is not another paragraph. 
  
| Fruits    | Tastiness |
|-----------|-----------|
| Apples    | Eh        |
| Mangoes   | Yummy     |
| Bananas   | So-So     |

As @tbl-sports-by-grade shows, ...

```{r}
#| label: tbl-sports-by-grade
#| tbl-cap: Mean sports played by grade
#| echo: true

popularity |>
  group_by(grade) |>
  summarize(mean_sports = mean(nsports)) |>
  gt() |>
  cols_label(grade = "Grade",
             mean_sports = "Mean sports played") |>
  fmt_number(mean_sports, decimals = 3)
```

```{r}
#| label: warning-example

as.numeric("A")
```

As @fig-sports-grade shows, sports participation goes down with age.

```{r}
#| label: fig-sports-grade
#| fig-cap: Violin plot showing relationship between number of sports played and grade in school.

ggplot(popularity, 
       aes(x = factor(grade), y = nsports))+
  geom_violin(fill = "darkgreen")+
  geom_jitter(alpha = 0.05)+
  labs(x = "grade in school", 
       y = "sports played")+
  theme_bw()
```