---
title: "Untitled"
author: Aaron Gullickson
format:
  html: default
  pdf: default
execute: 
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
#| output: false

library(tidyverse)
load("stat_data/popularity.RData")
```

# Compare number of sports by grade

## Second level header

### Third level header

#### Fourth level header

How do **number** of *sports* differ by _grade_ level?

- I don't know
- Another point
- Bob
  - Or Amanda?

1. First **point**
1. Second point
1. Third point

> I have sworn upon the altar of God eternal hostility against every form of tyranny over the mind of man

This is a paragraph.

This is another paragraph.

This is a paragraph.
  This is not another paragraph. 
  
| Fruits    | Tastiness |
|-----------|-----------|
| Apples    | Eh        |
| Mangoes   | Yummy     |
| Bananas   | So-So     |



```{r}
#| label: sports-by-grade
#| echo: true

popularity |>
  group_by(grade) |>
  summarize(mean_sports = mean(nsports))
```

```{r}
#| label: warning-example

as.numeric("A")
```